Document Expansion Using External Collections

### 2017-05-16 expansion/paper.tex
addressing comments and fixed float situation

\documentclass[sigconf]{acmart}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{verbatim}
\usepackage{colortbl}
%\usepackage[table]{xcolor}

@@

\setlist[itemize]{noitemsep}  % remove space between list items

@@

\author{Garrick Sherman}

\copyrightyear{2017}
\acmYear{2017}
\setcopyright{acmcopyright}
\acmConference{SIGIR '17}{}{August 7--11, 2017, Shinjuki, Tokyo, Japan}
\acmPrice{15.00.}
\acmDOI{http://dx.doi.org/10.1145/XXXXXXX.XXXXXXX}
\acmISBN{ISBN 978-1-4503-5022-8/17/08}

@@

Although Eq.~\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia\footnote{http://en.wikipedia.org}. We expect the latter, as a general encyclopedia, to yield relatively unbiased probability estimates. We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text.

We test our approach using TREC datasets:
\begin{itemize}
	\item The \textbf{AP} newswire collection from TREC disks 1 and 2 with topics 101-200.
	\item The \textbf{robust} 2004 topics, numbering 250, from TREC disks 4 and 5.
	\item The \textbf{wt10g} collection with the 100 topics from the 2000 and 2001 TREC Web tracks.
\end{itemize}

@@

For each collection, we produce eight runs representing a combination of expansion source and query expansion type.

We produce runs with expansion documents from:
\begin{itemize}
	\item the target collection itself, called \textit{self};
	\item Wikipedia, called \textit{wiki};
	\item a mixture of the previous two, called \textit{combined}; or
	\item no expansion, called \textit{baseline};
\end{itemize}

\noindent For each source, both the QL and RM3 variations are tested.

@@

\begin{table}[htb]
\centering
\begin{tabular}{|c|p{0.29\textwidth}|c|} \hline
{\bf Param.} & {\bf Meaning} & {\bf Value} \\ \hline
$k$ & The maximum number of document terms to use in constructing $Q_D$. & 20 \\ \hline
$n$ & The maximum number of expansion documents in $\mathcal{E}_D$. & 10 \\ \hline
$\lambda_{\mathcal{E}_D}$ & One of several related mixing parameters controlling the weights of $P(q|D)$ and $P(q|\mathcal{E}_D)$ & 0.0-1.0 \\ \hline
$\mu$ & Used for Dirichlet smoothing of both $P(q|D)$ and $P(q|E)$. & 2500 \\ \hline
$fbDocs$ & The number of feedback documents to use for RM3 runs. & 20 \\ \hline
$fbTerms$ & The number of terms per document to use for RM3 runs. & 20 \\ \hline
$\alpha$ & Mixing parameter controlling the weights of the original query and relevance model for RM3 runs. & 0.0-1.0 \\ \hline
\end{tabular}
\caption{Parameter settings for the document expansion procedure and retrieval model}
\label{table.parameters}
\end{table}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/expansion-sweep.pdf}
\caption{Sweeps over the number of expansion documents, $n = \{0, 1, 5, 10, 50\}$, for the \textit{self} and \textit{wiki} QL runs.}
\label{figure.n-sweeps}
\end{figure*}

\begin{table}
\begin{tabular}{|c|c|c|l|l|} \hline
{\bf Corpus} & {\bf \bigcell{l}{Exp. \\ Source}} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline\hline

\rule{0pt}{2.5ex} \multirow{8}{*}{AP} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2337 & \cellcolor{gray!50}0.4170 \\ \cline{3-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.3310$^{\underline{\uparrow}}$ & \cellcolor{gray!50}0.4855$^{\underline{\uparrow}}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2694$^{\underline{\uparrow}}$ & 0.4519$^{\underline{\uparrow}}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.3295$^{\underline{\uparrow *}}$ & \textbf{0.4876}$^{\underline{\uparrow *} W}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2644$^{\underline{\uparrow}}$ & 0.4582$^{\underline{\uparrow}}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it  RM3} & 0.3334$^{\underline{\uparrow *}}$ & 0.4811$^{\underline{\uparrow} *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.2774$^{\underline{\uparrow W}S}$ & 0.4734$^{\underline{\uparrow SW}}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.3342}$^{\underline{\uparrow *}\Uparrow S}$ & 0.4789$^{\underline{\uparrow}}$ \\ \hline\hline

\rule{0pt}{2.5ex} \multirow{8}{*}{Robust} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2183 & \cellcolor{gray!50}0.3867 \\ \cline{3-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.2639$^{\underline{\uparrow}}$ & \cellcolor{gray!50}0.3908$^{\underline{\uparrow}}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2369$^{\underline{\uparrow}}$ & 0.4036$^{\underline{\uparrow}}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.2591$^{\underline{\uparrow\Downarrow *}}$ & 0.3894$^{*}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2326$^{\underline{\uparrow}}$ & 0.4040$^\uparrow$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2674}$^{\underline{\uparrow *S}}$ & 0.4201$^{\underline{\uparrow\Uparrow S} *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.2417$^{\underline{\uparrow W}}$ & 0.4156$^{\underline{\uparrow\Uparrow W} S}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.2672$^{\underline{\uparrow *S}}$ & \textbf{0.4205}$^{\underline{\uparrow\Uparrow S}}$ \\ \hline\hline

\rule{0pt}{2.5ex} \multirow{8}{*}{wt10g} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.1683 & \cellcolor{gray!50}0.2816 \\ \cline{3-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.1651 & \cellcolor{gray!50}0.2834$^{\underline{\uparrow}}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.1660 & 0.2936 \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.1694$^\Uparrow$ & 0.2758$^\Downarrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.1780$^{\uparrow \underline{S}}$ & 0.3029$^\uparrow$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2089}$^{\underline{\uparrow\Uparrow *S}}$ & \textbf{0.3085}$^{\underline{\uparrow S}\Uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.1759$^{\uparrow\Uparrow S}$ & 0.3148$^{\underline{\uparrow\Uparrow} SW}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.2061$^{\underline{\uparrow\Uparrow *S}}$ & 0.3082$^{\underline{\uparrow\Uparrow S}}$ \\ \hline
\end{tabular}
\caption{Performance of runs using various expansion sources with (\textit{RM3}) and without (\textit{QL}) query expansion. Statistical significance at $p \leq 0.05$ is marked with a variety of symbols; underlining further designates $p \leq 0.01$: $\uparrow$ indicates improvement over the baseline QL run; $\Uparrow$ and $\Downarrow$ indicate improvement and decline respectively with respect to the baseline RM3 run; $^{*}$ indicates improvement over the QL run with the same expansion source; $^{S}$ and $^{W}$ indicate improvement over the \textit{self} and \textit{wiki} sources, respectively, of the same run type. Bolded runs are the highest raw score for an evaluation metric in a given collection.}
\label{table.effectiveness}
\end{table}

@@

@@

@@

The results indicate that our approach for document expansion works well in general and especially in concert with traditional relevance modeling. We find that we can improve on traditional document expansion by incorporating external collections into the expansion process. In the future, we plan to investigate in detail the relationship between homogeneity of documents and the effectiveness of our model.

>>>>

\documentclass[sigconf]{acmart}
\usepackage{afterpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{verbatim}
\usepackage{colortbl}
%\usepackage[table]{xcolor}

@@

\setcounter{topnumber}{8}
\setcounter{bottomnumber}{8}
\setcounter{totalnumber}{8}

@@

\author{Garrick Sherman}
\affiliation{School of Information Sciences\\University of Illinois at Urbana-Champaign}
\email{gsherma2@illinois.edu}
\author{Miles Efron}
\affiliation{School of Information Sciences\\University of Illinois at Urbana-Champaign}
\email{mefron@illinois.edu}

\copyrightyear{2017}
\acmYear{2017}
\setcopyright{acmlicensed}
\acmConference{SIGIR '17}{August 07-11, 2017}{Shinjuku, Tokyo, Japan}\acmPrice{15.00}\acmDOI{http://dx.doi.org/10.1145/3077136.3080716}
\acmISBN{978-1-4503-5022-8/17/08}

@@

Although Eq.~\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia\footnote{http://en.wikipedia.org}. We expect the latter, as a general encyclopedia, to yield relatively unbiased probability estimates. We build an Indri \cite{Strohman2005} index over the Wikipedia page text.

We test our approach using TREC datasets:
\begin{itemize}
	\item The \textbf{AP} newswire collection \cite{Harman1992} from TREC disks 1 and 2 with topics 101-200.
	\item The \textbf{robust} 2004 \cite{Voorhees2005} topics, numbering 250, from TREC disks 4 and 5.
	\item The \textbf{wt10g} collection \cite{Bailey2003} with the 100 topics from the 2000 and 2001 TREC Web tracks.
\end{itemize}

@@

For each collection, we produce eight runs representing a combination of expansion source and query expansion model. Expansion source refers to the collection(s) used for document expansion, while the query expansion model refers to unexpanded queries (QL) or expanded queries (RM3).

We produce runs with expansion documents from:
\begin{itemize}
	\item no expansion, called \textit{baseline};
	\item the target collection itself, called \textit{self};
	\item Wikipedia, called \textit{wiki}; or
	\item a mixture of the previous two, called \textit{combined}.
\end{itemize}

\noindent For each source, both the QL and RM3 variations are compared.

@@

\begin{table}[htb]
\caption{Parameter settings for the document expansion procedure and retrieval model}
\centering
\begin{tabular}{|c|p{0.29\textwidth}|c|} \hline
{\bf Param.} & {\bf Meaning} & {\bf Value} \\ \hline
$k$ & The maximum number of document terms to use in constructing $Q_D$. & 20 \\ \hline
$n$ & The maximum number of expansion documents in $\mathcal{E}_D$. & 10 \\ \hline
$\lambda_{\mathcal{E}_D}$ & One of several related mixing parameters controlling the weights of $P(q|D)$ and $P(q|\mathcal{E}_D)$ & 0.0-1.0 \\ \hline
$\mu$ & Used for Dirichlet smoothing of both $P(q|D)$ and $P(q|E)$. & 2500 \\ \hline
$fbDocs$ & The number of feedback documents to use for RM3 runs. & 20 \\ \hline
$fbTerms$ & The number of terms per document to use for RM3 runs. & 20 \\ \hline
$\alpha$ & Mixing parameter controlling the weights of the original query and relevance model for RM3 runs. & 0.0-1.0 \\ \hline
\end{tabular}
\label{table.parameters}
\end{table}

@@

\begin{table}[!ht]
\caption{Performance of runs using various expansion sources with (\textit{RM3}) and without (\textit{QL}) query expansion. Statistical significance at $p \leq 0.05$ is marked with a variety of symbols; underlining further designates $p \leq 0.01$: $\uparrow$ indicates improvement over the baseline QL run; $\Uparrow$ and $\Downarrow$ indicate improvement and decline respectively with respect to the baseline RM3 run; $^{*}$ indicates improvement over the QL run with the same expansion source; $^{S}$ and $^{W}$ indicate improvement over the \textit{self} and \textit{wiki} sources, respectively, of the same run type. Bolded runs are the highest raw score for an evaluation metric in a given collection.}
\begin{tabular}{|c|c|c|l|l|} \hline
{\bf Corpus} & {\bf \bigcell{l}{Exp. \\ Source}} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline

\rule{0pt}{2.5ex} \multirow{8}{*}{AP} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2337 & \cellcolor{gray!50}0.4170 \\ \cline{3-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.3310$^{\underline{\uparrow}}$ & \cellcolor{gray!50}0.4855$^{\underline{\uparrow}}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2694$^{\underline{\uparrow}}$ & 0.4519$^{\underline{\uparrow}}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.3295$^{\underline{\uparrow *}}$ & \textbf{0.4876}$^{\underline{\uparrow *} W}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2644$^{\underline{\uparrow}}$ & 0.4582$^{\underline{\uparrow}}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it  RM3} & 0.3334$^{\underline{\uparrow *}}$ & 0.4811$^{\underline{\uparrow} *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.2774$^{\underline{\uparrow W}S}$ & 0.4734$^{\underline{\uparrow SW}}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.3342}$^{\underline{\uparrow *}\Uparrow S}$ & 0.4789$^{\underline{\uparrow}}$ \\ \hline

\rule{0pt}{2.5ex} \multirow{8}{*}{Robust} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2183 & \cellcolor{gray!50}0.3867 \\ \cline{3-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.2639$^{\underline{\uparrow}}$ & \cellcolor{gray!50}0.3908$^{\underline{\uparrow}}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2369$^{\underline{\uparrow}}$ & 0.4036$^{\underline{\uparrow}}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.2591$^{\underline{\uparrow\Downarrow *}}$ & 0.3894$^{*}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2326$^{\underline{\uparrow}}$ & 0.4040$^\uparrow$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2674}$^{\underline{\uparrow *S}}$ & 0.4201$^{\underline{\uparrow\Uparrow S} *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.2417$^{\underline{\uparrow W}}$ & 0.4156$^{\underline{\uparrow\Uparrow W} S}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.2672$^{\underline{\uparrow *S}}$ & \textbf{0.4205}$^{\underline{\uparrow\Uparrow S}}$ \\ \hline

\rule{0pt}{2.5ex} \multirow{8}{*}{wt10g} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.1683 & \cellcolor{gray!50}0.2816 \\ \cline{3-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.1651 & \cellcolor{gray!50}0.2834$^{\underline{\uparrow}}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.1660 & 0.2936 \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.1694$^\Uparrow$ & 0.2758$^\Downarrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.1780$^{\uparrow \underline{S}}$ & 0.3029$^\uparrow$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2089}$^{\underline{\uparrow\Uparrow *S}}$ & \textbf{0.3085}$^{\underline{\uparrow S}\Uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.1759$^{\uparrow\Uparrow S}$ & 0.3148$^{\underline{\uparrow\Uparrow} SW}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.2061$^{\underline{\uparrow\Uparrow *S}}$ & 0.3082$^{\underline{\uparrow\Uparrow S}}$ \\ \hline
\end{tabular}
\label{table.effectiveness}
\end{table}

@@

%\afterpage{\clearpage}

@@

\begin{figure*}
\centering
\includegraphics[width=0.76\linewidth]{figures/expansion-sweep.pdf}
\caption{Sweeps over the number of expansion documents, $n = \{0, 1, 5, 10, 50\}$, for the \textit{self} and \textit{wiki} QL runs.}
\label{figure.n-sweeps}
\end{figure*}

@@

The results indicate that our approach for document expansion works well in general and especially in concert with traditional relevance modeling. We find that we can improve on traditional document expansion by incorporating external collections into the expansion process. In the future, we plan to investigate how important the choice of external collection is to the retrieval effectiveness of our model.
